Comparison of Confidence Interval in the OLS and Ridge Linear Regression Model: A Comparative study via Simulation

### 2024-08-27 draft_1.qmd
first draft

---
title: "Title"
format: #docx
    tandf-pdf:
      keep-tex: true  
    tandf-html: default
author:
  - name: Sultana Mubarika Rahman Chowdhury
    affiliations:
      - ref: biostat
    orcid: 
    email: schow034@fiu.edu
  - name: B.M Golam Kibria
    affiliations:
      - ref: stat
affiliations:
  - id: biostat
    name: Florida International University
    department: Biosatistics Department
    address: FIU
    city: Miami, Fl
    country: USA
    postal-code: 13210
  - id: stat
    name: Florida International University
    department: Department of Mathematics and Statistics
    address: FIU
    city: Miami, Fl
    country: USA
    postal-code: 13210
abstract: |
  Write down the abstract here
keywords: 
  - Ridge Regression
  - Multicolinearity
bibliography: bibliography.bib  
---

@@

# Ridge Regression

>>>>

---
title: "Comparison of Confidence Interval in the OLS and Ridge Linear Regression Model: A Comparative study via Simulation"
format: #docx
    tandf-pdf:
      keep-tex: true  
    tandf-html: default
author:
  - name: Sultana Mubarika Rahman Chowdhury
    affiliations:
      - ref: biostat
    orcid: 
    email: schow034@fiu.edu
  - name: B.M Golam Kibria
    affiliations:
      - ref: stat
  - name: Zoran Bursac
    affiliations:
      - ref: biostat
affiliations:
  - id: biostat
    name: Florida International University
    department: Biosatistics Department
    address: 11200 SW 8th St
    city: Miami, Fl
    country: USA
    postal-code: 33199
  - id: stat
    name: Florida International University
    department: Department of Mathematics and Statistics
    address: 11200 SW 8th St 
    city: Miami, Fl
    country: USA
    postal-code: 33199
abstract: |
  Write down the abstract here
keywords: 
  - Multiple Linear Regression
  - Ridge Regression
  - Multicolinearity
bibliography: bibliography.bib  
---

@@

Multiple linear regression maps the relationship between two or more predictors and dependent variable to a linear equation. The aim is to predict the response variable uisng the indepnedent variables. If X is a n×p full rank matrix of predictors and Y is a n × 1 vector of response variables the multiple linear regression can be explained as,

$$Y = X \times \beta + \epsilon$$,
where, $\beta$ is an p × 1 unknown regression paramaters and $\epsilon$ is the n × 1 vector of error with mean zero and equal variance.

One of the key assumption of the widely used multiple linear regression model is that the predictors need to be independent of each other. Violating the assumption of independence results in an issue known as multicollinearity. Multicollinearity occurs when two or more independent variables are highly correlated with each other. It causes standard error of the coefficient to increase resulting in wide confidence interval and less reliable results. Identifying significant predictors also becomes difficult.

# Statistical Methodology

## Ridge Regression Estimators

## Confidence Interval

### 2024-08-27 draft_1.tex
first draft

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Title},
  pdfauthor={Sultana Mubarika Rahman Chowdhury; B.M Golam Kibria},
  pdfkeywords={Ridge Regression, Multicolinearity},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Title}
\author{Sultana Mubarika Rahman Chowdhury$\textsuperscript{1}$, B.M
Golam Kibria$\textsuperscript{2}$}

\thanks{CONTACT: Sultana Mubarika Rahman
Chowdhury. Email: \href{mailto:schow034@fiu.edu}{\nolinkurl{schow034@fiu.edu}}. }
\begin{document}
\captionsetup{labelsep=space}
\maketitle
\textsuperscript{1} Biosatistics Department, Florida International
University, Miami, Fl, USA\\ \textsuperscript{2} Department of
Mathematics and Statistics, Florida International University, Miami,
Fl, USA
\begin{abstract}
Write down the abstract here
\end{abstract}
\begin{keywords}
\def\sep{;\ }
Ridge Regression\sep 
Multicolinearity
\end{keywords}

@@

\section{Ridge Regression}\label{ridge-regression}

>>>>

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Comparison of Confidence Interval in the OLS and Ridge Linear Regression Model: A Comparative study via Simulation},
  pdfauthor={Sultana Mubarika Rahman Chowdhury; B.M Golam Kibria; Zoran Bursac},
  pdfkeywords={Multiple Linear Regression, Ridge
Regression, Multicolinearity},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Comparison of Confidence Interval in the OLS and Ridge Linear
Regression Model: A Comparative study via Simulation}
\author{Sultana Mubarika Rahman Chowdhury$\textsuperscript{1}$, B.M
Golam Kibria$\textsuperscript{2}$, Zoran Bursac$\textsuperscript{1}$}

\thanks{CONTACT: Sultana Mubarika Rahman
Chowdhury. Email: \href{mailto:schow034@fiu.edu}{\nolinkurl{schow034@fiu.edu}}. }
\begin{document}
\captionsetup{labelsep=space}
\maketitle
\textsuperscript{1} Biosatistics Department, Florida International
University, Miami, Fl, USA\\ \textsuperscript{2} Department of
Mathematics and Statistics, Florida International University, Miami,
Fl, USA
\begin{abstract}
Write down the abstract here
\end{abstract}
\begin{keywords}
\def\sep{;\ }
Multiple Linear Regression\sep Ridge Regression\sep 
Multicolinearity
\end{keywords}

@@

One of the key assumption of the widely used multiple linear regression
model is that the predictors need to be independent of each other.
Violating the assumption of independence results in an issue known as
multicollinearity. Linear regression maps the relationship between the
predictors and dependent variable with a linear equation. If X is a n×p
full rank matrix of predictors and Y is a n × 1 vector of response
variables the multiple linear regression can be explained as,

\[Y = X \times \beta + \epsilon\], where, \(\beta\) is an p × 1 unknown
regression paramaters and \[\epsilon\] is the n × 1 vector of error with
mean zero and equal variance.\\
\# Statistical Methodology

\subsection{Ridge Regression
Estimators}\label{ridge-regression-estimators}
